---
title: "US Colleges Data Analysis"
output:
  pdf_document: default
  html_notebook: default
---

Usage of ggplot and Linear Regression Model to Answer the following questions:

1.  Do colleges with larger full time enrollments have lower graduation rates?

2.  Is this different for public and private institutions?

3.  If it is different for more selective schools?

**Know the Dataset**

```{r}
?College
glimpse(College)
```

**Exploratory Graphics to view Data**

```{r}
ggplot(College,aes(x=Grad.Rate))+geom_histogram() #Note Outlier
```

Making new filtered data frame to see suspicious college Grad rates

```{r}
suspicious <- filter(College,Grad.Rate>= 100)
View(suspicious)
```

**Analysis for Question 1**

Do colleges with larger full time enrollments have lower graduation rates?

Plotting a scatter plot between full time UG enrollments and Graduation Rates where the full time enrollments are in base 10

making a sub data frame called **college_sm** where the full time UG enrollments are in base 10 with selected attributes

```{r}
college_sm <- College %>%
  mutate(log_full=log10(F.Undergrad))%>%
  select(Grad.Rate,
         log_full,
         Private,
         Top25perc)

view(college_sm)
```

Plotting and Creating a model

```{r}
ggplot(College,aes(x=log10(F.Undergrad),y=Grad.Rate))+geom_point()+geom_smooth(method = "lm")
```

```{r}
model_undergrad <- lm(Grad.Rate ~ log_full,data=college_sm)
summary(model_undergrad)
```

The High p value and the flat line in the LR plot tells that maybe **full time undergradutes dont have a accurate description of the graduation rates.**

**Analysis For Question 2**

Is this different for public and private institutions?

adding a variable aesthetic of color in the scatter plot that differentiates between public and private institutions and adds a lm line to distinguish the trend

plot and model:

```{r}
ggplot(College,aes(x=log10(F.Undergrad),y=Grad.Rate,color=Private))+geom_point()+geom_smooth(method = "lm",se=FALSE)+scale_color_brewer(palette = 'Dark2')

model_private <- lm(Grad.Rate ~ Private + log_full,data=college_sm)
summary(model_private)
```

the low p value and the plot evidently shows that **a private college sees significantly higher grad rates compared to non-private colleges**

**Analysis For Question 3**

If it is different for more selective schools?

does the top25% of the universities make any difference about the graduation rates.

model and plots for the same:

```{r}
model_top <- lm(Grad.Rate ~ Private+log_full+Top25perc,data=college_sm)
summary(model_top)
plot(model_top)
```

**Summary**

as the p values for the top25% colleges is low hence they provide a accurate attribute for the graduation as well as the private vs public but the full time undergraduate rates dont have any effect on the graduation rate.
